Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_DNA_methylation.Rmd
meth - mod summary image chunk

```{r meth-igv, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/bismark-summary-report.png")
```

@@

The resulting could be used to mask the genome and the entire process described abo

>>>>

```{r meth-summary, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/bismark-summary-report.png")
```

@@

The resulting could be used to mask the genome and the entire process described above could be repeated (ie Genome Preparation, Alignment, Quantification)
